---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# report

> Generate reports from Rsquared Academy packages

[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/report)](https://cran.r-project.org/package=report) 
[![Travis-CI Build Status](https://travis-ci.org/rsquaredacademy/report.svg?branch=master)](https://travis-ci.org/rsquaredacademy/report) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rsquaredacademy/report?branch=master&svg=true)](https://ci.appveyor.com/project/rsquaredacademy/report)  ![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)

The goal of report is to generate automated reports for summary statistics,
RFM analysis, linear and logistic regression using the following packages:

- [descriptr](https://descriptr.rsquaredacademy.com)
- [rfm](https://rfm.rsquaredacademy.com)
- [olsrr](https://olsrr.rsquaredacademy.com)
- [blorr](https://blorr.rsquaredacademy.com)

## Installation

report is not available on CRAN yet. You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rsquaredacademy/report")
```

## Usage

Before generating the reports, it is important to ensure that the data used in the report is defined in the current session  i.e. when you run `ls()` in the console, the data must be listed by R. 

### Summary Statistics

```{r descriptr, eval=FALSE}
library(descriptr)
report_descriptr()
```

### RFM Analysis

```{r rfm, eval=FALSE}
rfm_data <- rfm::rfm_data_orders
report_rfm()
```

### Linear Regression

```{r olsrr, eval=FALSE}
model_data <- descriptr::mtcarz
report_ols()
```

### Logistic Regression

```{r blorr, eval=FALSE}
model_data <- blorr::bank_marketing
report_blr()
```

## Community Guidelines

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
