
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load, message=FALSE, echo=FALSE}
suppressWarnings(suppressMessages(library(olsrr, quietly = TRUE)))
```

<style type="text/css">
#best-subset-regression pre { /* Code block */
  font-size: 10px
}
</style>

<br>

## Regression

<br>

```{r regress}
ols_regress(model)
```

<br>

## Residual QQ Plot

<br>

```{r qqresid, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_resid_qq(model)
```

<br>

## Residual Normality Test

<br>

```{r normtest}
ols_test_normality(model)
```

<br>

Correlation between observed residuals and expected residuals under normality.

<br>

```{r corrtest}
ols_test_correlation(model)
```

<br>

## Residual vs Fitted Values Plot

<br>

```{r rvsfplot, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_resid_fit(model)
```

<br>

## Residual Histogram

<br>

```{r residhist, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_resid_hist(model)
```

<br>

## Cook's D Bar Plot

<br>

```{r ckdbp, fig.width=7, fig.height=5, fig.align='center'}
ols_plot_cooksd_bar(model)
```

<br>

## Cook's D Chart

<br>

```{r ckchart, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_cooksd_chart(model)
```

<br>

## DFBETAs Panel

<br>

```{r dfbpanel, fig.width=7, fig.height=7, fig.align='center'}
ols_plot_dfbetas(model)
```

<br>

## DFFITS Plot

<br>

```{r dfitsplot, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_dffits(model)
```

<br>

## Studentized Residual Plot

<br>

```{r srplot, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_resid_stud(model)
```

<br>

## Standardized Residual Chart

<br>

```{r srchart, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_resid_stand(model)
```

<br>

## Studentized Residuals vs Leverage Plot

<br>

```{r studlev, fig.width=7, fig.height=5, fig.align='center'}
ols_plot_resid_lev(model)
```

<br>

## Deleted Studentized Residual vs Fitted Values Plot

<br>

```{r dsrvsp, fig.width=7, fig.height=5, fig.align='center'}
ols_plot_resid_stud_fit(model)
```

<br>

## Hadi Plot

<br>

```{r hadiplot, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_hadi(model)
```

<br>

## Potential Residual Plot

<br>

```{r potres, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_resid_pot(model)
```

<br>

## Collinearity Diagnostics

<br>

### VIF

<br>

```{r viftol}
model <- lm(mpg ~ disp + hp + wt + qsec, data = mtcars)
ols_vif_tol(model)
```

<br>

### Condition Index

<br>

```{r cindex}
model <- lm(mpg ~ disp + hp + wt + qsec, data = mtcars)
ols_eigen_cindex(model)
```

<br>

### Collinearity Diagnostics

<br>

```{r colldiag}
model <- lm(mpg ~ disp + hp + wt + qsec, data = mtcars)
ols_coll_diag(model)
```

<br>

## Residual Fit Spread Plot

<br>

```{r rfsplot, fig.width=10, fig.height=5, fig.align='center'}
ols_plot_resid_fit_spread(model)
```

<br>

## Part & Partial Correlations

<br>

```{r partcor}
ols_correlations(model)
```

<br>

## Observed vs Predicted Plot

<br>

```{r obspred, fig.width=5, fig.height=5, fig.align='center'}
ols_plot_obs_fit(model)
```

<br>

### Diagnostics Panel

<br>

```{r diagpanel, fig.width=10, fig.height=10, fig.align='center'}
ols_plot_diagnostics(model)
```

<br>

## Added Variable Plot

<br>

```{r avplot, fig.width=10, fig.height=10, fig.align='center'}
ols_plot_added_variable(model)
```

<br>

## Residual Plus Component Plot

<br>

```{r cplusr, fig.width=10, fig.height=10, fig.align='center'}
ols_plot_comp_plus_resid(model)
```

<br>

## Breusch Pagan Test

<br>

```{r bp1}
ols_test_breusch_pagan(model)
```

<br>

## Score Test

<br>

```{r score1}
ols_test_score(model)
```

<br>

## F Test

<br>

```{r ftest1}
ols_test_f(model)
```

<br>

## All Possible Regression

<br>

```{r allsub}
ols_step_all_possible(model)
```

<br>

#### Plot

<br>

```{r allsubplot, fig.width=10, fig.height=10, fig.align='center'}
k <- ols_step_all_possible(model)
plot(k)
```

<br>

## Best Subset Regression

<br>

```{r bestsub, size='tiny'}
ols_step_best_subset(model)
```

<br>

#### Plot

<br>

```{r bestsubplot, fig.width=10, fig.height=10, fig.align='center'}
k <- ols_step_best_subset(model)
plot(k)
```

<br>

## Stepwise AIC Forward Regression

<br>

### Variable Selection

<br>

```{r stepaicf1}
ols_step_forward_aic(model)
```

<br>

### Plot

<br>

```{r stepaicf2, fig.width=5, fig.height=5, fig.align='center'}
k <- ols_step_forward_aic(model)
plot(k)
```

<br>

## Stepwise AIC Backward Regression

<br>

### Variable Selection

<br>

```{r stepaicb1}
k <- ols_step_backward_aic(model)
k
```

<br>

### Plot

<br>

```{r stepaicb2, fig.width=5, fig.height=5, fig.align='center'}
k <- ols_step_backward_aic(model)
plot(k)
```

<br>

## Stepwise AIC Regression

<br>

### Variable Selection

<br>

```{r stepwiseaic1}
ols_step_both_aic(model)
```

<br>

### Plot

<br>

```{r stepwiseaic2, fig.width=5, fig.height=5, fig.align='center'}
k <- ols_step_both_aic(model)
plot(k)
```
